---
title: |
  <center> Spatial determinants of home-range size in the Alpine wolf population </center>
subtitle: | 
  <center> an SCR analysis </center>
date: |
  <center> 22 April 2023 </center>
output:
  html_document: 
    fontsize: 11pt
    theme: "cerulean" 
    toc_depth: 2
    toc: yes
    toc_float: yes
    highlight: zenburn
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

```{=html}
<style>
div.assignment { background-color:#ffccff; border-radius:5px; padding:10px; }
</style>

<style>
div.exercise { background-color:#CCFFCC; border-radius:5px; padding:10px; }
</style>

<style>
div.question { background-color:#ffe5cc; border-radius:5px; padding:10px; }
</style>

<style>
div.time { background-color:#ffccff; border-radius:5px; padding:10px; }
</style>

<style>
div.background{ background-color:#e0e0e0; border-radius:5px; padding:10px; }
</style>

<style>
div.everyone{ background-color:#99FFFF; border-radius:5px; padding:10px; }
</style>

<style>
div.note { background-color:#FFFFCC; border-radius:5px; padding:10px; }
</style>
```




Pierre Dupont^1^ ([pierre.dupont\@nmbu.no](mailto:pierre.dupont@nmbu.no))
^1^ Faculty of Environmental Sciences and Natural Resource Management, PB 5003, NO-1432 Ås, Norway




## Introduction

The goal of this study is to quantify the variation in home range size in the wolf population of the Italian Alps and to identify the main drivers of this variation. To do so, we will perform a Spatial Capture-Recapture analysis of the data collected during the 2020/21 winter using **`nimbleSCR`**.

In a first attempt to estimate the spatial variation in home-range size of wolves using SCR, we will fit a model where $/sigma$, the scale parameter of the half-normal detection function varies as a function of a set of spatial covariates. In this instance, we will use the same set of spatial covariates in the density of Alpine wolves and $/sigma$.

::: note
**Note:** Because of the complexity of the model, we will first perform the analysis on a    subset of the dataset, namely wolf DNA samples that were collected in the regions of **Piemonte**, **Valle d'Aosta** and **Liguria**. 
:::
<br>




## Libraries and data

Again, we start by loading the R packages, custom functions and simulated data.
```{r, libraries, warning = FALSE, message = FALSE}
library(nimble)
library(nimbleSCR)
library(basicMCMCplots)
library(raster)
library(rgeos)
library(sf)
library(ggplot2)
library(ggplotify)
library(plotly)
library(data.table)
library(coda)
library(abind)
library(R.utils)
library(patchwork)
library(rnaturalearth)
library(rnaturalearthdata)
```

```{r, functions, warning = FALSE, message = FALSE}
source("workingDirectories.R")

##-- Source custom functions
sourceDirectory( "C:/My_documents/RovQuant/Temp/PD/nimbleSCR_workshop/functions",
                 modifiedOnly = F)
##-- Source custom functions
source( "C:/My_documents/AlpineWolf/Source/dbinomLocal_normal_SEM.R")
```

```{r, set-up specifications, warning = FALSE, message = FALSE}
##-- Model name and directories
modelName = "Piemonte.0.2"
thisDir <- file.path(analysisDir, "SpatialSigma/Piemonte")
dir.create(file.path(thisDir, modelName, "input"), recursive = T)
dir.create(file.path(thisDir, modelName, "output"), recursive = T)
dir.create(file.path(thisDir, modelName, "figures"), recursive = T)
```

```{r, load pre-processed data, warning = FALSE, message = FALSE}
##-- Load Alpine wolf dataset
load(file = file.path(thisDir, "data/Piemonte_data.RData"))

habitat.df <- habitat$ssdf
head(habitat.df)

detectors.df <- detectors$tdf
head(detectors.df)
detectors.df$detector <- detectors.df$id

data.df <- edf
head(data.df)

ind <- id.covs
head(ind)
```
<br>




## Visualizing the data

We use the **`plotNimbleSCR_input`** function to visualize the data.
```{r, plotNimbleSCR_input, warning = FALSE, message = FALSE, fig.align = 'center'}
input.plots <- plotNimbleSCR_input(
  data = data.df,
  habitat = habitat.df,
  detectors = detectors.df,
  detection.fun = c("dbinomLocal_normal"))
```

```{r, idDetections, out.width = "100%", fig.align = 'center'}
ggplotly(input.plots$detector.1.detections.by.individual)
```

We can also look at the spatial covariates contained in the **`habitat.df`** and **`detectors.df`** dataframes:
```{r, spatialCovs, out.width = "100%", warning = FALSE, fig.align = 'center'}
input.plots$habitat.cov.developed + 
  input.plots$habitat.cov.forest + 
  input.plots$habitat.cov.herbaceous + 
  input.plots$habitat.cov.bare.rock + 
  input.plots$habitat.cov.perpetual.snow + 
  input.plots$habitat.cov.alpine + 
  input.plots$habitat.cov.log_pop + 
  input.plots$habitat.cov.IUCN +
  input.plots$habitat.cov.mainRoads_L


input.plots$detector.1.cov.transect_L +
  input.plots$detector.1.cov.snow_fall +
  input.plots$detector.1.cov.pop +
  input.plots$detector.1.cov.transect_qi
```
<br>




## Write a **`nimbleSCR`** model w/ spatial covariates

We can now update the **`nimbleSCR`** model to account for the effects of spatial covariates on density and detectability.

First, we modify the **spatial process** section, which models the distribution of individual activity centers throughout the habitat, i.e. density.
In the basic SCR model, density was assumed to be constant. Here, we model density as a function of **forest cover**:

-   $D \sim bare rock + herbaceous + forest + pop + IUCN$

The **demographic process** section, which deals with the augmentation process is unchanged.

To account for spatial variation in the **detection process**, we model the baseline detection probability ($p_0$) at each detector location as a function of the **search effort**:

-   $p_0 \sim transect_L + transect_{qi} + snowfall + log(pop)$

-   $\sigma \sim \sim bare rock + herbaceous + forest + pop + IUCN$

-   $p_{ij} = p_{0} \, \exp\Big{(}-\frac{d_{ij}^2}{2\sigma^2}\Big{)}$

```{r, model}
## ------   1. MODEL ------
modelCode <- nimbleCode({
  ##---- SPATIAL PROCESS  
  for(c in 1:numHabCovs){
    betaHab[c] ~ dnorm(0.0,0.01)
  }#c
  
  habIntensity[1:numHabWindows] <- exp(
    habCovs[1:numHabWindows,1:numHabCovs] %*% betaHab[1:numHabCovs])
  sumHabIntensity <- sum(habIntensity[1:numHabWindows])
  logHabIntensity[1:numHabWindows] <- log(habIntensity[1:numHabWindows])
  logSumHabIntensity <- log(sumHabIntensity)
  
  for(i in 1:M){
    s[i,1:2] ~ dbernppAC(
      lowerCoords = lowerHabCoords[1:numHabWindows,1:2],
      upperCoords = upperHabCoords[1:numHabWindows,1:2],
      logIntensities = logHabIntensity[1:numHabWindows],
      logSumIntensity = logSumHabIntensity,
      habitatGrid = habitatGrid[1:numHabGridRows,1:numHabGridCols],
      numGridRows = numHabGridRows,
      numGridCols = numHabGridCols)
  }#i
  
  
  ##---- DEMOGRAPHIC PROCESS  
  psi ~ dunif(0,1)
  rho ~ dunif(0,1)
  
  for(ss in 1:2){
    theta[1:numStates,ss] ~ ddirch(alpha[1:numStates,ss])
  }#ss
  
  for(i in 1:M){ 
    z[i] ~ dbern(psi) 
    indCovs[i,1] ~ dbern(rho)                              # sex[i] ~ dbern(rho)
    indCovs[i,2] ~ dcat(theta[1:numStates,indCovs[i,1]+1]) # status[i] ~ dcat(theta[1:n.states,sex[i]+1])
  }#i 	
  

  
  ##---- DETECTION PROCESS 
  ##-- Priors for p0 and sigma intercepts
  for(s in 1:numStates){
    for(ss in 1:2){
      p0[s,ss] ~ dunif(0,0.5)
      sigma0[s,ss] ~ dunif(0,2)
      logit(p0Traps[s,ss,1:numTraps]) <- logit(p0[s,ss]) + 
        trapCovs[1:numTraps,1:numTrapCovs] %*% betaTraps[1:numTrapCovs]
    }#ss
  }#s
  
  ##-- Priors for regression coefficients on p0
  for(c in 1:numTrapCovs){
    betaTraps[c] ~ dnorm(0.0,0.01)
  }#c
  
  ##-- Priors for regression coefficients on sigma
  for(c in 1:numHabCovs){
    betaSigma[c] ~ dnorm(0.0,0.01)
  }#c
  
  betaDens ~ dnorm(0.0,0.01)

  
  ##-- 
  for(i in 1:M){
    y[i,1:lengthYCombined] ~ dbinomLocal_normal_SEM(
      resizeFactor = 1,
      size = size[1:numTraps],
      p0Traps = p0Traps[indCovs[i,2],indCovs[i,1]+1,1:numTraps],
      sigma0 = sigma0[indCovs[i,2],indCovs[i,1]+1],
      densCov = densCov[1:numHabWindows],
      betaDens = betaDens,
      habCovs = habCovs[1:numHabWindows,1:numHabCovs],
      betaHab = betaSigma[1:numHabCovs],
      s = s[i,1:2],
      trapCoords = trapCoords[1:numTraps,1:2],
      localTrapsIndices = localTrapsIndices[1:numHabWindows,1:localTrapsNumMax],
      localTrapsNum = localTrapsNum[1:numHabWindows],
      habitatGrid = habitatGrid[1:numHabGridRows,1:numHabGridCols],
      indicator = z[i],
      lengthYCombined = lengthYCombined)
  }#i
  
  
  
  ##---- POPULATION SIZE & DENSITY
  ## ABUNDANCE
  N <- sum(z[1:M])
  
  ## Number of individuals in each habitat cell
  density[1:numHabWindows] <- calculateDensity(
    s = s[1:M,1:2],
    habitatGrid = habitatGrid[1:numHabGridRows,1:numHabGridCols],
    indicator = z[1:M],
    numWindows = numHabWindows,
    nIndividuals = M)
  
  densCov[1:numHabWindows] <- log(density[1:numHabWindows]+1) - 0.2
})
```
<br>




## Formatting the data

Here, we use the **`data2nimbleSCR`** wrapper function to help us format the input data.
We simply have to specify which covariate(s) we want to use in the model by providing their names to the function.
```{r, data formatting}
##-- Format input for nimbleSCR
nimInput <- data2nimbleSCR(
  data = data.df,
  ind = ind,
  ind.covs = c("sex","status"),
  habitat = habitat.df,
  habitat.covs = c( "bare rock",
                    "herbaceous",
                    "forest",
                    "pop",
                    "IUCN"),
  detectors = detectors.df,
  detectors.covs = c( "transect_L", 
                      "transect_qi", 
                      "snow_fall", 
                      "log_pop"),
  detectors.dmax = 80000,
  detection.fun = "dbinomLocal_normal",
  M = 2500)

##-- Add number of states to the constants
nimInput$constants$alpha <- matrix(1,3,2)
nimInput$constants$numStates <- 3
```

The **`nimInput`** object now also contains two spatial covariates (**`habCovs`** and **`trapCovs`**).
::: note
Remember to also provide initial values for the new parameters in the model **`betaHab`** and **`betaTraps`**!
:::
```{r, initial values, eval = FALSE}
##-- Generate initial values for "z"
z.init <- rbinom(n = nimInput$constants$M, 1, prob = 0.4)
z.init[nimInput$data$y[,1]>0] <- 1

##-- Generate initial values for "s"
s.init <- getSInits(
  y = nimInput$data$y,
  trapCoords = as.matrix(nimInput$data$trapCoords),
  lowerCoords = as.matrix(nimInput$data$lowerHabCoords),
  upperCoords = as.matrix(nimInput$data$upperHabCoords),
  habitatGrid = as.matrix(nimInput$data$habitatGrid),
  lengthYCombined = nimInput$constants$lengthYCombined)

##-- Generate initial values for "sex"
sex.init <- rbinom(n = nimInput$constants$M, 1, prob = 0.5)
sex.init[!is.na(nimInput$data$indCovs[ ,"sex"])] <- NA

##-- Generate initial values for "status"
status.init <- rcat(n = nimInput$constants$M, prob = c(0.3,0.6,0.1))
status.init[!is.na(nimInput$data$indCovs[ ,"status"])] <- NA

##-- Add to the input
nimInput$inits <- list( 
  psi = 0.6,
  rho = 0.5,
  theta = cbind(c(0.5,0.45,0.05),
                c(0.5,0.3,0.2)),
  sigma0 = cbind(c(0.5,0.5,1),
                 c(0.5,0.5,1)),
  p0 = cbind(c(0.1,0.1,0.05),
             c(0.1,0.1,0.05)),
  betaHab = rnorm(nimInput$constants$numHabCovs),
  betaSigma = rnorm(nimInput$constants$numHabCovs),
  betaTraps = rnorm(nimInput$constants$numTrapCovs),
  z = c(rep(1,nimInput$constants$M*0.6),
        rep(1,nimInput$constants$M*0.4)),
  s = s.init[ , ,1],
  indCovs = cbind(sex.init, status.init))
```

```{r, save input, warning = FALSE, echo = FALSE}
for(c in 1:8){
  ##-- Generate initial values for "z"
  z.init <- rbinom(n = nimInput$constants$M, 1, prob = 0.4)
  z.init[nimInput$data$y[,1]>0] <- 1
  
  ##-- Generate initial values for "s"
  s.init <- getSInits(
    y = nimInput$data$y,
    trapCoords = as.matrix(nimInput$data$trapCoords),
    lowerCoords = as.matrix(nimInput$data$lowerHabCoords),
    upperCoords = as.matrix(nimInput$data$upperHabCoords),
    habitatGrid = as.matrix(nimInput$data$habitatGrid),
    lengthYCombined = nimInput$constants$lengthYCombined)
  
  ##-- Generate initial values for "sex"
  sex.init <- rbinom(n = nimInput$constants$M, 1, prob = 0.5)
  sex.init[!is.na(nimInput$data$indCovs[ ,"sex"])] <- NA
  
  ##-- Generate initial values for "status"
  status.init <- rcat(n = nimInput$constants$M, prob = c(0.3,0.6,0.1))
  status.init[!is.na(nimInput$data$indCovs[ ,"status"])] <- NA
  
  ##-- Add to the input
  nimInput$inits <- list( 
    psi = 0.6,
    rho = 0.5,
    theta = cbind(c(0.5,0.45,0.05),
                  c(0.5,0.3,0.2)),
    sigma0 = cbind(c(0.5,0.5,1),
                   c(0.5,0.5,1)),
    p0 = cbind(c(0.1,0.1,0.05),
               c(0.1,0.1,0.05)),
    betaHab = rnorm(nimInput$constants$numHabCovs),
    betaSigma = rnorm(nimInput$constants$numHabCovs),
    betaDens = 0,
    betaTraps = rnorm(nimInput$constants$numTrapCovs),
    z = c(rep(1,nimInput$constants$M*0.6),
          rep(1,nimInput$constants$M*0.4)),
    s = s.init[ , ,1],
    indCovs = cbind(sex.init, status.init))
  
  ##-- Save nimbleSCR input
  save( modelCode, nimInput, 
       file = file.path( thisDir, modelName, "input",
                         paste0(modelName, "_input_", c, ".RData")))
}
```
<br>




## Fitting the model

Now we are ready to fit the model in **`nimble`**.
::: note
Don't forget to provide the names of the additional parameters in the list of tracked parameters!
:::
```{r, modFit, warning = FALSE, message = FALSE, eval = FALSE}
##-- Create the nimble model object
nimModel <- nimbleModel( code = modelCode,
                         constants = nimInput$constants,
                         inits = nimInput$inits,
                         data = nimInput$data,
                         check = FALSE,
                         calculate = FALSE) 
nimModel$calculate()

##---- Compile the nimble model object to C++
CsimModel <- compileNimble(nimModel)
CsimModel$calculate()

##---- Configure and compile the MCMC object 
conf <- configureMCMC( model = nimModel,
                       monitors = c("N", "betaHab", "betaTraps","betaSigma","betaDens",
                                        "sigma0","psi","p0","density"),
                       thin = 1,
                       monitors2 = c("density","s","z","indCovs"))
Rmcmc <- buildMCMC(conf)
compiledList <- compileNimble(list(model = nimModel, mcmc = Rmcmc))
Cmodel <- compiledList$model
Cmcmc <- compiledList$mcmc

##---- Run nimble MCMC in multiple bites
for(c in 1:1){
  print(system.time(
    runMCMCbites( mcmc = Cmcmc,
                  bite.size = 100,
                  bite.number = 2,
                  path = file.path(thisDir, modelName, paste0("output/chain",c)))
  ))
}


```

```{r, debug, warning = FALSE, message = FALSE, eval = FALSE}
nimModel$calculate()
  
nimModel$logProb_y

i <- 19
dbinomLocal_normal_SEM(
  x = nimModel$y[i, ],
  resizeFactor = 1,
  size = nimModel$size,
  p0Traps = nimModel$p0Traps[nimModel$indCovs[i,2],nimModel$indCovs[i,1]+1, ],
  sigma0 = nimModel$sigma0[nimModel$indCovs[i,2],nimModel$indCovs[i,1]+1],
  densCov = nimModel$densCov,
  betaDens = 0,
  habCovs = nimModel$habCovs,
  betaHab = nimModel$betaSigma,
  s = nimModel$s[i,1:2],
  trapCoords = nimModel$trapCoords,
  localTrapsIndices = nimModel$localTrapsIndices,
  localTrapsNum = nimModel$localTrapsNum,
  habitatGrid = nimModel$habitatGrid,
  indicator = nimModel$z[i],
  lengthYCombined = nimInput$constants$lengthYCombined,
  log = 1)


```

```{r, loadFit,  message = FALSE, echo = FALSE}
#-- save output for later
# save(nimOutput, runtime, file ="nimOutput2.RData")
niter <- 11000
nburnin <- 1000
nchains <- 2 

#-- load saved output
load(file ="nimOutput2.RData")
```

This SCR model with covariates took approx.
`r round(runtime[3]/60)` min to run `r nchains` chains of `r niter` iterations.
<br>




## Processing the output

Here, we can inspect parameter traceplots and summarize the posteriors. The trace plots on the left show the MCMC sample values throughout fitting process.
Density plots on the right represent the posterior distribution of the different parameters.
```{r, posterior estimate, warning = FALSE}

##---- Collect multiple MCMC bites and chains
nimOutput <- collectMCMCbites( path = file.path(thisDir, modelName, "output"),
                               burnin = 0,
                               pattern = "mcmcSamples",
                               param.omit = NULL,
                               progress.bar = F)

##---- Traceplots
pdf(file = file.path(thisDir,  modelName, "figures", paste0(modelName, "_traceplots.pdf")))
plot(nimOutput$samples)
graphics.off()

##-- Traceplots and density plots for the tracked parameters
chainsPlot( nimOutput,
            var = c("N","p0","sigma","psi","betaHab","betaTraps"),
            line = c(N, p0, sigma, psi, betaHab, betaTraps))

##-- Summary of posteriors
summary <- summary(nimOutput)$statistics
summary[c("N","p0","sigma","psi","betaHab","betaTraps"), ]
```

And we also process the output for more convenient use.
```{r, more output processing, out.width = "100%", warning = FALSE, message = FALSE}
procOutput <- ProcessCodaOutput(nimOutput, DIC = F)
```
<br>




## Population density

We use the **`plotNimbleSCR_output`** function to generate and compare density maps.
If provided with the simulated density alues, **`plotNimbleSCR_output`** can make maps of true and estimated densities.
```{r, output plots, message = FALSE, warning = FALSE}
output.plots <- plotNimbleSCR_output( procOutput = procOutput,
                                      habitat.df = habitat.df,
                                      true.density = true.density)
```

In addition, we use the habitat grid from  **`output.plots`** to calculate and map predicted density based on covariate values. 
```{r, predicted density, out.width = "100%",  warning = FALSE, fig.align = 'center'}
##-- Calculate mean predicted density per habitat cell
habitat.sf <- output.plots$misc.data$habitat.sf
habitat.sf$pred.density <- exp(log(procOutput$mean$N/
                                     sum(exp(procOutput$mean$betaHab*nimInput$data$habCovs))) +
                                 procOutput$mean$betaHab*nimInput$data$habCovs)

##-- Plot predDensity
p3 <- ggplot() + 
  geom_sf( data = habitat.sf,
           aes_string(fill = habitat.sf$pred.density)) +
  scale_color_viridis_c(na.value = "white")+
  scale_fill_viridis_c(na.value = "white")+
  ggtitle("Predicted density") +
  theme( panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank())

p3 + output.plots$estimated.density.surface + output.plots$true.density.surface
```

And we extract population size for the area covered by the detector grid, i.e., the study area with the habitat buffer removed.
```{r, cropped map, out.width = "90%",  warning = FALSE, fig.align = 'center'}
##-- Mask the density surface with the desired focal area
focal.sf <- input.plots$misc.data$detector.stuff$effort$detector.poly.sf
density.r <- habitat.r <- output.plots$misc.data$habitat.r
density.inside.r <- mask(density.r, focal.sf)
habitat.sf$cropped.density <- density.inside.r[!is.na(habitat.r)]

##-- Cropped density
ggplot() + 
  geom_sf( data = habitat.sf,
           aes_string(fill = habitat.sf$cropped.density)) +
  scale_color_viridis_c(na.value = "white")+
  scale_fill_viridis_c(na.value = "white")+
  ggtitle("Cropped density") +
  theme( panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank())

```

Using the SCR model with spatial covariates, the abundance inside the study area is estimated to be **`sum(density.inside.r[], na.rm = TRUE)`** = `r round(sum(density.inside.r[], na.rm = TRUE),1)`
Further, because **`nimbleSCR`** models allow tracking the location and status of each individual separately, we can plot the estimated AC location against the simulated one for each detected individual:
```{r, individual maps, out.width = "100%",  warning = FALSE, fig.align = 'center'}
output.plots <- plotNimbleSCR_output( procOutput,
                                     habitat.df,
                                     true.ACs = true.s,
                                     individuals = c("2","9","11","12","16","23"))

output.plots$estimated.and.true.AC.locations +
  # Adding the outline of the study area to the plot
  geom_sf(data = st_union(input.plots$misc.data$detector.stuff$effort$detector.poly.sf),
          color = "white", fill = NA)
```
<br>




## Effect plots

Using posterior samples, we can predict the density and baseline detection probability for different covariate values. 
We can then plot the relationship between the covariates and the variable of interest (with associated uncertainty). First, we look at predicted density.
```{r, effect plots1, out.width = "90%",  warning = FALSE, fig.align = 'center'}
##-- Covariate values to predict for
newCov <- seq( min(nimInput$data$habCovs),
               max(nimInput$data$habCovs),
               length.out = 200)

##-- Calculate posterior predicted density
posterior_D <- sapply(1:length(procOutput$sims.list$N),
                      function(x){ exp(log(procOutput$sims.list$N[x]/
                                             sum(exp(procOutput$sims.list$betaHab[x] * nimInput$data$habCovs))) + procOutput$sims.list$betaHab[x] * newCov)})

##-- Make a prediction data.frame
pred <- cbind.data.frame(
  "x" = seq(0,100,length.out = 200),
  "mean" = apply(posterior_D, 1, mean),
  "lci" = apply(posterior_D, 1, function(x) quantile(x,0.025)),
  "uci" = apply(posterior_D, 1, function(x) quantile(x,0.975)))

##-- Plot predicted density
ggplot( data = pred,
        aes(y = mean, x = x)) +
  ylab( label = "Density (ids/100km2)") +
  xlab( label = "Forest cover (%)") + 
  geom_ribbon( aes(ymin = lci, ymax = uci),
               fill = "firebrick4",
               alpha = 0.3) +
  geom_line( color = "firebrick4",
             lwd = 1.2) +
  ggtitle("Predicted density") 

```

Next, we look at the predicted baseline detection probability ($p_0$).
```{r, effect plots2, out.width = "90%",  warning = FALSE, fig.align = 'center'}
##-- Covariate values to predict for
newCov <- seq( min(nimInput$data$trapCovs),
               max(nimInput$data$trapCovs),
               length.out = 200)

##-- Calculate posterior predicted density
posterior_p0 <- sapply(1:length(procOutput$sims.list$p0),
                       function(x){  ilogit(logit(procOutput$sims.list$p0[x]) +
                                              procOutput$sims.list$betaTraps[x] * newCov)})

##-- Make a prediction data.frame
pred <- cbind.data.frame(
  "x" = newCov,
  "mean" = apply(posterior_p0, 1, mean),
  "lci" = apply(posterior_p0, 1, function(x) quantile(x,0.025)),
  "uci" = apply(posterior_p0, 1, function(x) quantile(x,0.975)))

##-- Plot predicted baseline detecyion probability
ggplot( data = pred,
        aes(y = mean, x = x)) +
  ylab( label = bquote(p[0])) +
  xlab( label = "Search effort") + 
  geom_ribbon( aes(ymin = lci, ymax = uci),
               fill = "firebrick4",
               alpha = 0.3) +
  geom_line( color = "firebrick4",
             lwd = 1.2) +
  ggtitle("Baseline detection probability") 
```
<br>




## Detectability map

We use the detector grid contained in **`input.plots`** to make a map of detector-specifc $p_0$ values. 
```{r, detectability map, out.width = "90%", warning = FALSE, fig.align = 'center'}
##-- Find the detector grid
detector.grid <- input.plots$misc.data$detector.stuff$effort$detector.poly.sf

##-- Calculate mean predicted p0 per detector
detector.grid$p0 <- ilogit(logit(procOutput$mean$p0) + procOutput$mean$betaTraps * nimInput$data$trapCovs)

##-- Plot map of p0
ggplot() + 
  geom_sf( data = habitat.sf,
           fill = adjustcolor("green",0.2)) +
  geom_sf( data = detector.grid,
           aes_string(fill = detector.grid$p0)) +
  scale_color_viridis_c( na.value = "white")+
  scale_fill_viridis_c( na.value = "white")+
  ggtitle( bquote(Detectability ~ (p[0]))) +
  theme( panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank())
```
<br>


